---
title: "Visualizing Star Wars characters"
author: "Siyu(ish)"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
```

1.  Glimpse at the starwars data frame.

```{r}
#| label: glimpse-starwars

glimpse(starwars)
```

2.  Modify the following plot to change the color of all points to `"pink"`.

```{r}
#| label: scatterplot

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "pink")
```

3.  Add labels for title, x and y axes, and size of points. Uncomment to see the effect.

```{r}
#| label: scatterplot-labels

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(
    title = "The height and mass of Starwars characters",
    x = "height", 
    y = "mass",
    point = " birth year"
    )
```

4.  Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it.

(A little bit of starter code is provided below, and the code chunk is set to not be evaluated with `eval: false` because the current code in there is not valid code and hence the document wouldn't knit. Once you replace the code with valid code, set the chunk option to `eval: true`, or remove the `eval` option altogether since it's set to `true` by default.)

```{r}
#| label: histogram

ggplot(data = starwars, mapping = aes(x=height)) +
  geom_histogram(binwidth = 3)+
  facet_wrap(~sex)
```

5.  Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: num-cat
ggplot(data = starwars, mapping = aes(x=height, y=gender, color=species)) +
  geom_point()
```

This is a plot of Star Wars characters heights in relation to their gender. The color of the points indicate different species. 

6.  Pick a single categorical variable from the data set and make a bar plot of its distribution.

```{r}
#| label: barplot
ggplot(data=starwars)+
  geom_bar(mapping = aes(x=hair_color))
```

7.  Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: cat-cat
ggplot(data = starwars, mapping = aes(x=eye_color, y=homeworld, color=sex)) +
  geom_point()
```

In the graph above, the x-axis is eye color and the y-axis is home world of the characters. Each point is a character. The color of the points stands for the sex of the characters. 

8.  Pick two numerical variables and two categorical variables and make a visualization that incorporates all of them and provide an interpretation with your answer.

(This time no starter code is provided, you're on your own!)

```{r}
#| label: multi
ggplot(data = starwars, mapping = aes(x=sex, y=height, color=hair_color, size=birth_year)) +
  geom_point()+
  geom_smooth()

  
```

In the graph above, the x-axis is sex, and the y-axis is the height. Each point is a character from the Stat Wars series. The colors of the points stand for the hair color of the characters, and the size of the points stands for the birth year of the characters. 